; This file allows you to customize the context menu options available
; when right-clicking on mapspots while PAW is active.
; 
; enable: setting this to false will hard-killswitch an option to off
; mode 	: controls when the option is shown, see below
; text	: translation string to display in the menu option
; act 	: the action executed by the option - currently only pn_add
;	 		has any use beyond the existing option for that action
; icon 	: forces use of this icon - only for action pn_add
; func 	: functor to execute, passing args
; funcN : any N number of additional functors, each will receive args 

; The args passed to the functors include the object ID of the target
; (if there was one), and all attributes of the action itself.

;  Modes: 
;     -1: only when debug mode is enabled
;      0: disabled completely
;      1: enabled in normal view only
;      2: enabled in cartography mode only
;      4: enabled in both

; ==================================================

[my_stash_icon]

; This is an example of how you can add a 
; new menu option that drops a pin with a
; specific icon. It is disabled by default.
;
; To make your own:
; 1. Make a copy of everything between the ==
;    lines, including the [my_stash_icon]
;    section name at the top.
; 2. Rename the section to something unique
;    (different from any other in this file).
; 3. Change enable to true.
; 4. Choose any valid icon from icons.ltx and
;    replace stash_green with that.
; 5. Change the mode number, if desired.
; 6. Edit the text as desired - this can be 
; 	 either a string literal as in the example,
; 	 or the ID of a valid translation string as 
; 	 in most of the default functions.
;
; Your new quick pin option should now appear 
; in the context menu when you right-click on
; any mapspot. You can make more than one as 
; long as each has a unique section name.

mode 		= 4
enable 		= false
text 		= "Place stash icon"
act 		= pn_add
func 		= tasks_placeable_waypoints.func_pn_add
icon 		= bwhr_stash
colors 		= 255, 100, 100, 255

; Color values (in order) are Alpha, Red, Green, Blue
; 
; Using the bwhr_stash icon instead of a normal stash
; icon will give you the freedom to customize its
; color. But if you just want the usual green icon, 
; you can remove the "colors" line above, and change 
; "bwhr_stash" to "stash_green" (or any valid icon).
;
; NOTE: this file will be overwritten when PAW is
; updated. Back up your customizations.

; ==================================================
; Another useful example:
[tag_signal_source]
; I often use PAW to mark where I encountered beeps or
; other signals when hunting with the RF receiver--seeing
; these on the map can really help visualize where the 
; target actually is.
mode 		= 4
enable 		= false
; As before, change enable to true if you want to use 
; this custom action.
text 		= "Signal source contact"
act 		= pn_add
func 		= tasks_placeable_waypoints.func_pn_add
icon 		= bwhr_signal
; ==================================================


[mping]
; Ping the map
mode        = 2
enable      = true
text        = ui_mcm_pawsys_pawmenu_mping
act 		= mping
func 		= tasks_placeable_waypoints.ping_area_around

[wp_set]
; Set a new waypoint here when one does not exist yet
mode        = 4
enable      = true
text        = ui_mcm_pawsys_pawmenu_wp_set
act         = wp_set
func 		= tasks_placeable_waypoints.func_wp_set

[wp_mov]
; Move an existing waypoint to here
mode        = 4
enable      = true
text        = ui_mcm_pawsys_pawmenu_wp_mov
act         = wp_mov
func 		= tasks_placeable_waypoints.func_wp_mov

[wp_del]
; Remove the existing waypoint
mode        = 4
enable      = true
text        = ui_mcm_pawsys_pawmenu_wp_del
act         = wp_del
func 		= tasks_placeable_waypoints.func_wp_del

[pn_add]
; Add a new map pin
mode        = 4
enable      = true
text        = ui_mcm_pawsys_pawmenu_pn_add
act         = pn_add
func 		= tasks_placeable_waypoints.func_pn_add
func1 		= tasks_placeable_waypoints.func_pn_settings

[pn_del]
; Delete a map pin
mode        = 4
enable      = true
text        = ui_mcm_pawsys_pawmenu_pn_del
act         = pn_del
func 		= tasks_placeable_waypoints.func_pn_del

[pn_settings]
; Open Pin Settings window
mode        = 4
enable      = true
text        = ui_mcm_pawsys_pawmenu_pn_settings
act         = pn_settings
func 		= tasks_placeable_waypoints.func_pn_settings

[wp_settings]
; Open Waypoint Settings window
mode        = 4
enable      = true
text        = ui_mcm_pawsys_pawmenu_wp_settings
act         = wp_settings
func 		= tasks_placeable_waypoints.open_waypoint_settings

[hud_vis_on]
; Shows a pin on the HUD
mode        = 2
enable      = true
text        = ui_mcm_pawsys_pawmenu_hud_vis_on
act         = hud_vis_on
func 		= tasks_placeable_waypoints.func_hud_vis_on

[hud_vis_off]
; Hides a pin from the HUD
mode        = 4
enable      = true
text        = ui_mcm_pawsys_pawmenu_hud_vis_off
act         = hud_vis_off
func 		= tasks_placeable_waypoints.func_hud_vis_off

[show_all_pins]
; Show pins if hidden
mode        = 2
enable      = true
text        = ui_mcm_pawsys_pawmenu_show_all_pins
act         = show_pins
func 		= tasks_placeable_waypoints.func_show_all_pins

[hide_all_pins]
; Hides pins if shown
mode        = 2
enable      = true
text        = ui_mcm_pawsys_pawmenu_hide_all_pins
act         = hide_pins
func 		= tasks_placeable_waypoints.func_hide_all_pins

[lock_pin]
; Lock pin to prevent changes
mode        = 2
enable      = true
text        = ui_mcm_pawsys_pawmenu_lock_pin
act         = lock_pin
func 		= tasks_placeable_waypoints.func_lock_pin

[unlock_pin]
; Unlock pin
mode        = 4
enable      = true
text        = ui_mcm_pawsys_pawmenu_unlock_pin
act         = unlock_pin
func 		= tasks_placeable_waypoints.func_unlock_pin

[show_label]
; Show a hint-like label/caption banner above pin on PDA map
mode        = 2
enable      = true
text        = ui_mcm_pawsys_pawmenu_show_label
act         = show_label
func 		= tasks_placeable_waypoints.func_show_pin_label

[hide_label]
; Hide the label/caption banner
mode        = 4
enable      = true
text        = ui_mcm_pawsys_pawmenu_hide_label
act         = hide_label
func 		= tasks_placeable_waypoints.func_hide_pin_label

[convert_to_pin]
mode        = 4
enable      = true
text        = ui_mcm_pawsys_pawmenu_convert_to_pin
act         = convert_to_pin
func 		= tasks_placeable_waypoints.func_convert_to_pin

[pn_clr]
; Clear all map pins - no confirmation!
; Disabled by default, set mode nonzero to enable
mode        = 0
enable      = true
text        = ui_mcm_pawsys_pawmenu_pn_clr
act         = pn_clr
func 		= tasks_placeable_waypoints.func_pn_clr

[clear_nearby]
; Clear all nearby map pins - no confirmation!
; radius definable, measured from clicked spot
mode        = 2
enable      = true
text        = ui_mcm_pawsys_pawmenu_clear_nearby
act         = clear_nearby
func 		= tasks_placeable_waypoints.clear_nearby_pins

;[cm_dbg]
; Debug menu -- currently deprecated
;mode        = -1
;enable      = false
;text        = ui_mcm_pawsys_pawmenu_cm_dbg
;act         = cm_dbg

